### 2017-04-14 paper/oopsla17-submission/evaluation.tex
asd

\section{Evaluation}
\label{sec:evaluation}
\input{data}

@@

\subsection{Methodology}
\label{sec:methodology}

@@

\paragraph{Feature Selection}
We extract a set of 277 features from each sub-expression in a student
program, including:
%
\begin{enumerate}
\item 44 local syntactic features. In addition to the syntax of \lang,
  we support the full range of arithmetic operators (integer and
  floating point), equality and comparison operators, character and
  string literals, and a user-defined |expr| type of simple arithmetic
  expressions. We discuss the challenge of supporting other
  user-defined types in \autoref{sec:discussion}.
\item 176 contextual syntactic features. For each sub-expression we
  additionally extract the local syntactic features of its parent and
  first, second, and third (left-to-right) children. If an expression
  does not have a parent or children, these features will simply be
  disabled. If an expression has more than three children, the
  classifiers will receive no information about the additional
  children.
\item 55 typing features. In addition to the types of \lang, we support
  |int|s, |float|s, |char|s, |string|s, and the user-defined |expr|
  mentioned above. These features are extracted for each sub-expression
  and for the contextual sub-expressions.
\item One feature denoting the size of each sub-expression.
\item One feature denoting whether each sub-expression is part of the
  minimal type error slice. We use this feature as a ``hard''
  constraint, sub-expressions that are not part of the minimal slice
  will be preemptively discarded. We justify this decision in
  \autoref{sec:feature-utility}.
\end{enumerate}

\paragraph{Blame Oracle}
Recall from \autoref{sec:labels} that we automatically extract a blame
oracle for each ill-typed program from the (AST) diff between it and the
student's eventual fix.
%
A disadvantage of using diffs in this manner is that students may have
made many, potentially unrelated, changes between compilations; at some
point the ``fix'' becomes a ``rewrite''.
%
We do not wish to consider the ``rewrites'' in our evaluation, so we
discard outliers where the fraction of expressions that have changed is
more than one standard deviation above the mean, establishing a diff
threshold of 44\%.
%
This accounts for roughly 14\% of each dataset, leaving us with
2,425 program pairs for \SPRING and 2,325 pairs for \FALL.

@@

\paragraph{Accuracy Metric}
All of the tools we compare (with the exception of the standard \ocaml
compiler) can produce a list of potential error locations.
%
However, in a study of fault localization techniques,
\citet{Kochhar2016-oc} show that most developers will not consider more
than around five potential error locations before falling back to manual
debugging.
%
Type errors are relatively simple in comparison to general fault
localization, thus we limit our evaluation to the top three predictions
of each tool.
%
We evaluate each tool on whether a changed expression occurred in its
top one, top two, or top three predictions.

>>>>

\section{Quantitative Evaluation}
\label{sec:evaluation}
\input{data}

@@

\mysubsection{Methodology}
\label{sec:methodology}

@@

\mypara{Feature Selection}
We extract a set of 277 features from each sub-expression in a student
program, including:
%
\begin{enumerate}
\item 44 local syntactic features. In addition to the syntax of \lang,
  we support the full range of arithmetic operators (integer and
  floating point), equality and comparison operators, character and
  string literals, and a user-defined |expr| type of simple arithmetic
  expressions. We discuss the challenge of supporting other
  user-defined types in \autoref{sec:discussion}.
\item 176 contextual syntactic features. For each sub-expression we
  additionally extract the local syntactic features of its parent and
  first, second, and third (left-to-right) children. If an expression
  does not have a parent or children, these features will simply be
  disabled. If an expression has more than three children, the
  classifiers will receive no information about the additional
  children.
\item 55 typing features. In addition to the types of \lang, we support
  |int|s, |float|s, |char|s, |string|s, and the user-defined |expr|
  mentioned above. These features are extracted for each sub-expression
  and for the contextual sub-expressions.
\item One feature denoting the size of each sub-expression.
\item One feature denoting whether each sub-expression is part of the
  minimal type error slice. We use this feature as a ``hard''
  constraint, sub-expressions that are not part of the minimal slice
  will be preemptively discarded. We justify this decision in
  \autoref{sec:feature-utility}.
\end{enumerate}

\mypara{Blame Oracle}
Recall from \autoref{sec:labels} that we automatically extract a blame
oracle for each ill-typed program from the (AST) diff between it and the
student's eventual fix.
%
A disadvantage of using diffs in this manner is that students may have
made many, potentially unrelated, changes between compilations; at some
point the ``fix'' becomes a ``rewrite''.
%
We do not wish to consider the ``rewrites'' in our evaluation, so we
discard outliers where the fraction of expressions that have changed is
more than one standard deviation above the mean, establishing a diff
threshold of 44\%.
%
This accounts for roughly 14\% of each dataset, leaving us with
2,425 program pairs for \SPRING and 2,325 pairs for \FALL.

@@

\mypara{Accuracy Metric}
All of the tools we compare (with the exception of the standard \ocaml
compiler) can produce a list of potential error locations.
%
However, in a study of fault localization techniques,
\citet{Kochhar2016-oc} show that most developers will not consider more
than around five potential error locations before falling back to manual
debugging.
%
Type errors are relatively simple in comparison to general fault
localization, thus we limit our evaluation to the top three predictions
of each tool.
%
We evaluate each tool on whether a changed expression occurred in its
top one, top two, or top three predictions.

### 2017-04-14 paper/oopsla17-submission/learning.tex
shuffle
asd

\input{feature-table}

@@

\paragraph{Logistic Regression.} The simplest classifier we investigate is logistic regression. This is a linear model, where the goal is to learn a set of weights $W$ and a bias $b$ that describe the following model for predicting a label $y$ from a feature vector $x$:
\[ \Pr(y = 1 | x) = \frac{1}{1 + e^{-W^{\top} x - b}} \]
The weights $W$ and $b$ are learnt from training data, and the value of $\Pr(y | x)$ naturally leads to a confidence score. Logistic regression is a widely used classification algorithm, which is largely preferred for its simplicity, ease of generalization as well as interpretability. Its main limitation is that the prediction rule is constrained to be a linear combination of the features, and hence relatively simple. While this can be somewhat mitigated by adding higher order (quadratic or cubic) features, this often requires substantial domain knowledge.

@@

\paragraph{Decision Trees.} Decision tree algorithms learn a tree of binary predicates over the features, recursively partitioning the input space until a final
classification can be made. Each node in the tree contains a single predicate of the form
$v_j \leq t$ for some feature $v_j$ and threshold $t$, which determines
whether a given input should proceed down the left or right subtree.
Each leaf is labeled with a prediction and the fraction of training
samples that would reach it, the latter quantity can be interpreted as
\ES{HUMA: is this correct?}
the decision tree's confidence in its prediction. This leads to a prediction rule
that can be quite expressive depending on the data used to build it.

@@

\paragraph{Random Forests.} Random forests mitigate the generalization problem by training an {\em{ensemble}} of distinct decision trees and then using a majority vote to make a prediction. The agreement among the distinct trees in the ensemble forms a natural confidence score. Since each classifier in the ensemble is a decision tree, this still allows for complex and highly expressive classifiers. \ES{Huma: is this the confidence score that we are using?}

@@

\paragraph{Neural Networks}
The last (and most complex) model we use is a type of neural network
called a \emph{multi-layer perceptron} (see \citealt{Nielsen2015-pu} for
an introduction to neural networks).

>>>>

@@

\mypara{Logistic Regression.} The simplest classifier we investigate is logistic regression. This is a linear model, where the goal is to learn a set of weights $W$ and a bias $b$ that describe the following model for predicting a label $y$ from a feature vector $x$:
\[ \Pr(y = 1 | x) = \frac{1}{1 + e^{-W^{\top} x - b}} \]
The weights $W$ and $b$ are learnt from training data, and the value of $\Pr(y | x)$ naturally leads to a confidence score. Logistic regression is a widely used classification algorithm, which is largely preferred for its simplicity, ease of generalization as well as interpretability. Its main limitation is that the prediction rule is constrained to be a linear combination of the features, and hence relatively simple. While this can be somewhat mitigated by adding higher order (quadratic or cubic) features, this often requires substantial domain knowledge.

@@

\mypara{Decision Trees.} Decision tree algorithms learn a tree of binary predicates over the features, recursively partitioning the input space until a final
classification can be made. Each node in the tree contains a single predicate of the form
$v_j \leq t$ for some feature $v_j$ and threshold $t$, which determines
whether a given input should proceed down the left or right subtree.
Each leaf is labeled with a prediction and the fraction of training
samples that would reach it, the latter quantity can be interpreted as
\ES{HUMA: is this correct?}
the decision tree's confidence in its prediction. This leads to a prediction rule
that can be quite expressive depending on the data used to build it.

@@

\mypara{Random Forests.} Random forests mitigate the generalization problem by training an {\em{ensemble}} of distinct decision trees and then using a majority vote to make a prediction. The agreement among the distinct trees in the ensemble forms a natural confidence score. Since each classifier in the ensemble is a decision tree, this still allows for complex and highly expressive classifiers. \ES{Huma: is this the confidence score that we are using?}

@@

\mypara{Neural Networks}
The last (and most complex) model we use is a type of neural network
called a \emph{multi-layer perceptron} (see \citealt{Nielsen2015-pu} for
an introduction to neural networks).
